Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-06-07 SIR_manuscript.tex
clean up broken itemized list

\item {\bf A potential advantage of slow test reporting $\omega$, result~\ref{p1:omega};}

@@

\item {\bf The counter-vailing effect of \percap testing intensity, $\rho$, on $\Rnum$;}
- The explanation here is that more rapid testing leaves more susceptibles in the ``waiting-for-no'' $S\_n$ category at the DFE and delay them to get to $I\_c$ where they are subject to a full isolation, thus no transmission.
- We are missing out on community-level advantages of fast testing.
- What is the explanation for having this counter-vailing effect of $\rho$ in targeted testing and not in the random one?
- May because in the targeted testing more $I\_u$s are tested compared to $S\_u$s, given 
 that higher $\omega$ leaves more people in $S\_n$ and $I\_n$ which results in more transmission.
- While targeted testing strategies, including targeting people with infection-like symptoms or the contacts of confirmed cases, are always more effective than random testing, as expected, we find that in some cases the direct effect of testing is that viral spread is greater for a slow test than for a fast test. This counter-intuitive effect can occur when people are cautious when awaiting a test result, and may not be robust to second-order effects of fast testing (such as better contact tracing).

\item {\bf Specifying the compartment-specific relative testing weights, Specifically $\frac{w_I}{w_S}$;}

@@

\item What can we say in the context of strength and speed paradigm?

\end{enumerate}

>>>>

{\bf A potential advantage of slow test reporting $\omega$, result~\ref{p1:omega};}

@@

{\bf The counter-vailing effect of \percap testing intensity, $\rho$, on $\Rnum$;}
- The explanation here is that more rapid testing leaves more susceptibles in the ``waiting-for-no'' $S\_n$ category at the DFE and delay them to get to $I\_c$ where they are subject to a full isolation, thus no transmission.
- We are missing out on community-level advantages of fast testing.
- What is the explanation for having this counter-vailing effect of $\rho$ in targeted testing and not in the random one?
- May because in the targeted testing more $I\_u$s are tested compared to $S\_u$s, given 
 that higher $\omega$ leaves more people in $S\_n$ and $I\_n$ which results in more transmission.
- While targeted testing strategies, including targeting people with infection-like symptoms or the contacts of confirmed cases, are always more effective than random testing, as expected, we find that in some cases the direct effect of testing is that viral spread is greater for a slow test than for a fast test. This counter-intuitive effect can occur when people are cautious when awaiting a test result, and may not be robust to second-order effects of fast testing (such as better contact tracing).

{\bf Specifying the compartment-specific relative testing weights, Specifically $\frac{w_I}{w_S}$;}

@@

What can we say in the context of strength and speed paradigm?
